Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2021-02-22 09.0_manuscript.rmd
ground hog works with one package at a time

```{r, include=FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
pacman::p_load(knitr, pander, citr, broom)
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

```{r setup, echo = FALSE}
library(knitr)
opts_knit$set(eval.after = "fig.cap")
```

>>>>

```{r setup1, include=FALSE, echo = FALSE}
if (!require("groundhog", quietly=TRUE)) install.packages("groundhog"); library(groundhog)
groundhog.day = "2020-05-01"
# pkgs=c('knitr', 'pander', 'citr', 'broom')
groundhog.library('knitr', groundhog.day)
groundhog.library('pander', groundhog.day)
# groundhog.library('citr', groundhog.day)
groundhog.library('broom', groundhog.day)

# options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

```{r setup2, echo = FALSE}
library(knitr)
opts_knit$set(eval.after = "fig.cap")
```

### 2021-02-22 10.0_Supporting_Information.Rmd
ground hog works with one package at a time

```{r setup, include=FALSE, echo = FALSE}
if(!require("pacman", quietly=TRUE)) install.packages("pacman")
suppressPackageStartupMessages(
  pacman::p_load(bookdown, knitr, pander, citr, broom))
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
# load("results/manuWorkSpace.RData")
# install.packages(c("vctrs", "rlang"))
```

>>>>

```{r setup1, include=FALSE, echo = FALSE}
if (!require("groundhog", quietly=TRUE)) install.packages("groundhog"); library(groundhog)
groundhog.day = "2020-05-01"
# pkgs=c('knitr', 'pander', 'citr', 'broom')
groundhog.library('knitr', groundhog.day)
groundhog.library('pander', groundhog.day)
# groundhog.library('citr', groundhog.day)
groundhog.library('broom', groundhog.day)
options(tinytex.verbose = TRUE)
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
```
